### 2014-04-07 ApTranscriptome_TR.Rmd
Writing

$$ TPM = \beta_0 + \beta_1(colony) + \beta_2(temp) + \beta_3(temp^2) + \beta_4(colony * temp) + \\beta_5(colony * temp^2) + \epsilon $$

@@

pandoc.table(Ap.type.table, style="rmarkdown", caption = "Number of transcripts with maximum expression at high, low, intermediate or both high and low (bimodal) temperatures.")

# only transcripts that differ in expression by colony
A22.interaction.type.table <- table(interaction.response.type[ , 'A22.type'])
Ar.interaction.type.table <- table(interaction.response.type[ , 'Ar.type'])

Ap.interaction.type.table <- rbind(A22.interaction.type.table, Ar.interaction.type.table)
rownames(Ap.interaction.type.table) <- c("A22", "Ar")

pandoc.table(Ap.interaction.type.table, style="rmarkdown", caption = "For transcripts that differ in expression pattern between *A22* and *Ar*, the number of transcripts with maximum expression at high, low, intermediate or both high and low (bimodal) temperatures.")

@@

# T-test comparing standard deviation of expression between colonies
t.test(A22.int.sd$exp_sd, Ar.int.sd$exp_sd)
```

@@

# t-test to compare standard deviation of 'Bimodal' transcripts between colonies
t.test(A22.bim.sd, Ar.bim.sd)
```

@@

Probability distribution function of peak expression for transcripts that differ in expression between *A22* and *Ar*

```{r max_exp_PDF}
# reshape data
Ap.df <- data.frame(Transcript = rep(Ap.response.type$Transcript, times = 2), colony = rep(c("A22", "Ar"), each = length(Ap.response.type$Transcript)), max.val = c(Ap.response.type$A22.max, Ap.response.type$Ar.max))

@@

```{r partition_reaction_norm_variation}
# take absolute value of each value and sum to get total differences between reaction norms
varshape.out$s.total <- abs(varshape.out$s.offset) + abs(varshape.out$s.slope) + abs(varshape.out$s.curvature) + abs(varshape.out$s.wiggle)

@@

mean(varshape.out$prop.mean)
mean(varshape.out$prop.slope)
mean(varshape.out$prop.curve)
mean(varshape.out$prop.wiggle)
```

>>>>

$$ log(TPM + 1) = \beta_0 + \beta_1(colony) + \beta_2(temp) + \beta_3(temp^2) + \beta_4(colony * temp) + \beta_5(colony * temp^2) + \epsilon $$

@@

# re-orderfor printing
Ap.type.table <- Ap.type.table[ , c(2,4,1,3,5)]

pandoc.table(Ap.type.table, style="rmarkdown", caption = "Number of thermally-responsive transcripts with maximum expression at high, low, intermediate, both high and low (bimodal) temperatures or are not expressed for each colony.")

# Pearson Chi-square test
chisq.test(Ap.type.table)
```

@@

# T-test comparing standard deviation of expression between colonies
t.test(Ar.int.sd$exp_sd, A22.int.sd$exp_sd)
```

@@

# t-test to compare standard deviation of 'Bimodal' transcripts between colonies
t.test(Ar.bim.sd, A22.bim.sd)
```

@@

Probability density function of peak expression for transcripts that differ in expression between *A22* and *Ar*

```{r max_exp_PDF}
# reshape data
Ap.df <- data.frame(Transcript = rep(Ap.response.type$Transcript, times = 2), colony = rep(c("ApVT", "ApNC"), each = length(Ap.response.type$Transcript)), max.val = c(Ap.response.type$A22.max, Ap.response.type$Ar.max))

@@

```{r partition_reaction_norm_variation}
# weighted mean-standardized values of each measure
mean(abs((varshape.out$s.offset)))
mean(abs((varshape.out$s.slope)))
mean(abs((varshape.out$s.curvature)))
mean(abs((varshape.out$s.wiggle)))

# take absolute value of each value and sum to get total differences between reaction norms
varshape.out$s.total <- abs(varshape.out$s.offset) + abs(varshape.out$s.slope) + abs(varshape.out$s.curvature) + abs(varshape.out$s.wiggle)

@@

# Mean proportion and 95% CI of total variation of each measure
mean(varshape.out$prop.mean)
quantile(varshape.out$prop.mean, probs = c(0.05, 0.5, 0.95))

mean(varshape.out$prop.slope)
quantile(varshape.out$prop.slope, probs = c(0.05, 0.5, 0.95))

mean(varshape.out$prop.curve)
quantile(varshape.out$prop.curve, probs = c(0.05, 0.5, 0.95))

mean(varshape.out$prop.wiggle)
quantile(varshape.out$prop.wiggle, probs = c(0.05, 0.5, 0.95))
```
